Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-05-17 mard-survey.tex
2015.05.16 (Alex & Vassilis) Extensive re-wording throughout the paper. Abstract on its one file. Better figure scaling and alignment. Re-ordering of algorithms in the histogram figures to match paper order of appearence and the table ordering.

@@

\author{Vassilis Moustakas,
        H\"useyin Akcan,
        Mema Roussopoulos,
        and~Alex Delis,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{Vassilis Moustakas, Mema Roussopoulos and Alex Delis are with the Department
of Informatics and Telecommunications, National and Kapodistrian University of Athens,
GR15784, Athens, Greece (e-mails: {vsmoustakas,mema,ad}@di.uoa.gr.}% <-this % stops a space
\thanks{H\"useyin Akcan is with the Department of Software Engineering,
Izmir University of Economics, Izmir, Turkey (email: huseyin.akcan@ieu.edu.tr).}% <-this % stops a space
\thanks{Manuscript received June 30, 2015; revised July 31, 2015.}}

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
\emph{Peer-to-peer} (\p) systems have enjoyed immense attention and have been
widely deployed on the Internet for well ov, er a decade.
They are implemented via an overlay network abstraction, on top 
of the Internet's best-effort IP infrastructure. 
\p\ systems support a plethora of desirable features to
distributed applications that are built on top of them including
anonymity, high availability and robustness, 
load balancing, quality of service, scalability, to name just a few.
Unfortunately, inherent weaknesses of early deployments of \p\ systems, prevented 
applications from leveraging the full potential of the paradigm.
One major weakness, identified early on, is the \emph{topology mismatch problem}
between the overlay network and the underlying IP topology.
This mismatch can impose an extraordinary amount of unnecessary stress on
network resources and can adversely affect the scalability and efficiency of
applications built atop.
In this paper, we survey over a decade's worth of research efforts
aimed at alleviating the topology mismatch problem, in both unstructured
and structured \p\ systems.   
We provide a fine-grained categorization of the suggested solutions
by discussing their novelty, advantages and weaknesses.
Finally, we offer an analysis as well as pictorial comparisons 
of the reviewed approaches, since we aim to offer a comprehensive
reference for developers, system architects and researchers in the field.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Distributed systems, peer-to-peer, overlay network, topology mismatch,
topology awareness
\end{IEEEkeywords}

>>>>

\usepackage{comment}

@@

\author{Vassilis Moustakas,
        H\"useyin Akcan,
        Mema Roussopoulos,
        and~Alex Delis,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{Vassilis Moustakas, Mema Roussopoulos and Alex Delis are 
	with the Department of Informatics and Telecommunications, 
	\emph{University of Athens},
GR15784, Athens, Greece, e-mails: \emph{\{vsmoustakas,mema,ad\}@di.uoa.gr}}% <-this % stops a space
\thanks{H\"useyin Akcan is with the Department of Software Engineering,
\emph{Izmir University of Economics}, 35330 Balcova, Izmir, Turkey, email: \emph{huseyin.akcan@ieu.edu.tr}}% <-this % stops a space
\thanks{Manuscript received April 30, 2015; revised April 30, 2015.}}

@@

\input{abstract}
